intro

### 2021-10-29 06_Paper/ER-ED/intro.Rmd
added text on ER flexibility and transition to SVs

[...]
<!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
To 
For example it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011].  
<!-- Kommentare zu  ER Choice -->
[...]
<!-- Überleitung zu SVs-->
What was missing in this research so far was the information regarding the strategy not chosen. 
People choose a strategy that they prefer, for whatever reason. 
However, nothing is revealed about the strategy that is not chosen.
On the one hand, it could be possible that the chosen strategy is the clear preference, the unchosen strategy is not a realistic option for the individual. 
On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
<!-- Evtl. Forschung zum Repertoire --> 
Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

>>>>

[...]
<!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous facotrs.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.

<!-- Weitere Einflussfaktoren aufzuählen zu  ER Choice -->
[...]

What was missing in this research so far was the information regarding the strategy not chosen. 
People choose a strategy that they prefer, for whatever reason. 
However, nothing is revealed about the strategy that is not chosen.
On the one hand, it could be possible that the chosen strategy is the clear preference, the unchosen strategy is not a realistic option for the individual. 
On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
This leads to the question of how individual subjective values of ER strategies are characterized an how one can determine them. 
Individual subjective values (SV) of effortful tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
